% the sample slide is created with 16:9 aspect ratio
\documentclass[aspectratio=169]{beamer}

% remove the options if you do not want to have them
\usetheme[
	background=hanyang,
	logo="logo.png",
	logo2 = "logo2.png"
]{hanyang}

% the background and logo are in the images directory
\graphicspath{{images/}}

% information for the title page
\author{성민창}
\title{\textbf{LABMEETING}}
\subtitle{An unofficial theme for Hanyang University}
\institute{바이오로보틱스 연구실}
\date{\today}

\begin{document}
	% use plain option to remove the page number from the title slide
	\begin{frame}[plain]
		\titlepage
	\end{frame}

	\begin{frame}{Introduction}
	안녕하세요 저는 성민창입니다.
		\begin{itemize}
			\item \textbf{가나다라마바사}
				\begin{itemize}
					\item \textbf{가}: 1st January 1957
					\item \textbf{나}: 2,569.69 $\text{km}^2$
					\item \textbf{다}: 695m (Dolberg in Hunsrück)
					\item \textbf{라}: 995,597 (31st December 2015)
					\item \textbf{마}: 6.5\% (June 2017)
				\end{itemize}
			\item \textbf{가나다라마바사}
				\begin{itemize}
					\item \textbf{가}: 1st January 1957
					\item \textbf{나}: 2,569.69 $\text{km}^2$
					\item \textbf{다}: 695m (Dolberg in Hunsrück)
					\item \textbf{라}: 995,597 (31st December 2015)
					\item \textbf{마}: 6.5\% (June 2017)
				\end{itemize}
			\item Credits: \url{https://tjdalsckd.github.io/}
		\end{itemize}
	\end{frame}

	\begin{frame}{Blocks}
		%\framesubtitle{This is a subtitle}
		\begin{block}{Standard Block}
			This is a standard block.
		\end{block}
		
		\begin{exampleblock}{Example Block}
			This is an example block.
		\end{exampleblock}
		
		\begin{alertblock}{Alert Block}
			This is an alert block.
		\end{alertblock}
	\end{frame}
	
	\begin{frame}{Math}
		Mathematics is the queen of sciences and arithmetic is the queen of mathematics.
		\begin{align*}
			\Pr(Y \geq 120) &= \Pr\left(Y-n\mu \geq 120-n\mu \right)\\
			&= \Pr\left( \frac{Y-n\mu }{\sqrt{n}\sigma} \geq \frac{120-n\mu }{\sqrt{n}\sigma} \right)\\
			&=\Pr\left( Z \geq \frac{120-n\mu }{\sqrt{n}\sigma} \right)\\
			&=\Pr\left( Z \geq \frac{120-100 \cdot 1 }{10 \cdot 1} \right)\\
			&=\Pr\left( Z \geq 2\right)
		\end{align*}
	\end{frame}

	\begin{frame}{Two Columns}
		We can also add two columns in the slides. `asdfasfd' and ``asdf''
 		\begin{columns}[t]
			\begin{column}[T]{0.4\textwidth}
				This is the first column. In this column, we can also add a block for instance.
				\vspace{1em}
				\begin{block}{Block}
					I am a block in a column.
				\end{block}
			\end{column}
			\begin{column}[T]{0.4\textwidth}
				\begin{itemize}
					\item In this column,
					\item we just add the
					\item bullet points.
				\end{itemize}
			\end{column}
		\end{columns}
	\end{frame}
	\begin{frame}{Acknowledgements}
		This theme is inspired by saarland theme. The official beamer user guide was also very handy during the development.
	\end{frame}
\end{document}
